Cloud Manufacturing Ecosystem - Scheduling And Evolving

### 2015-10-02 schedule.tex
20150927
give up simulation

% !TEX root = Eco-Model.tex
\section{Resources Scheduling} % (fold)
\label{sec:model}

In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the resources scheduling process in Cloud Manufacturing Ecosystem.

@@

\subsection{Rating Schema} % (fold)
\label{sub:rating_schema}

% subsection rating_schema (end)

\subsection{Recommand System} % (fold)
\label{sub:recommand_system}

% subsection recommand_system (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Services Scheduling} % (fold)
\label{sec:schedule}

In order to properly accomplish the proposed tasks with optimal allocation of the manufacturing resources, a series of methodologies were combined to assist the manufacturing services scheduling process in Cloud Manufacturing Ecosystem, since manufacturing serivices are contrusted from manufacturing resources.

OAS

@@
